Attrition in Online Learning: Understanding Persistence and Dropout in Massive Open Online Courses

### 2014-10-29 paper_v1.Rnw
adding pred analysis

Table \ref{tab:s1sum} provides summary statistics for enrollment, survey response rates, demographics, self-reported dropout, and three behavioral indicators for each course. The behavioral indicators represent course milestones: the proportions of learners who viewed over 30\%, 50\%, and 80\% of lecture videos in the course. The data illustrated in Figure \ref{fig:s1reason} reflect the proportions of learners who selected each reason relative to all learners who reportedly stopped participating in each course. The correlation matrixes in Tables \ref{tab:s1reascor} and \ref{tab:s1cor2} are a linear combination of correlation matrixes for each course, assigning equal weight to all courses to discount for considerable variation in sample sizes.

@@

>>>>

Table \ref{tab:s1sum} provides summary statistics for enrollment, survey response rates, demographics, self-reported dropout, and three behavioral indicators for each course. The behavioral indicators represent course milestones: the proportions of learners who viewed over 30\%, 50\%, 80\% of lecture videos and attempted over 30\%, 50\%, 80\% of assessments in the course. In addition, to capture performance, we  The data illustrated in Figure \ref{fig:s1reason} reflect the proportions of learners who selected each reason relative to all learners who reportedly stopped participating in each course. The correlation matrixes in Tables \ref{tab:s1reascor} and \ref{tab:s1cor2} are a linear combination of correlation matrixes for each course, assigning equal weight to all courses to discount for considerable variation in sample sizes.

@@

<<>>=
res = read.csv("pred_coefs.csv")
ggplot(subset(res, coef2!="Intercept"), aes(coef2, est, ymin=est-1.96*se, ymax=est+1.96*se, color=factor(sign))) + 
  geom_hline(xintercept=0) + geom_pointrange() + facet_wrap(~y, ncol=4) + coord_flip() + 
  theme_minimal() + theme(legend.position="none",axis.title=element_text(vjust=0)) + 
  scale_color_manual(values=c('red','grey30','darkgreen')) +
  labs(y="Estimated change in probability (95% CIs)", x="")
@
